Response to the defense feedback

### 2021-06-15 Chapter-4/Chapter-4.tex
Updates from Overleaf

\section{Problem}
In Chapter~\ref{chapter3}, we present a method to identify address-based side-channel leakage sites in cryptography libraries ~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}. However, many reported leakage sites are not patched by developers. Recent work on side-channel vulnerability identification~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} also faced the same situation. For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@. Further analysis shows 1,510 leaks can be dismissed. But that leaves 460 data-access leaks and 278 control-flow leaks. Many of these vulnerabilities have not been fixed by developers for a variety of reasons.

First, some vulnerable implementations perform better. For example,
RSA implementations usually adopt the CRT optimization, which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}. Second, fixing vulnerabilities can introduce new
weaknesses. Third, most vulnerabilities pose a negligible risk. Although some vulnerabilities result in the key being entirely compromised~\cite{184415, aumuller2002fault}, many others are less severe in reality. Therefore, we need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.

@@

To overcome these limitations, we propose a novel method to quantify information
leakage precisely. We quantify the number of bits that can leak during a real
execution and define the amount of leaked information as the cardinality of
possible secrets based on an attacker's observation. Before an attack, an adversary has a large but finite input space.
Whenever the adversary observes a leakage site, they can eliminate some impossible
inputs and reduce the input space's size. In an extreme case, if the input space's size reduces to one, an adversary has determined the input, which means all secret information (e.g., the entire secret key) is
leaked. By counting the number of inputs~\cite{10.1007/11499107_24}, we can quantify the information leakage precisely.
We use symbolic execution to generate constraints to model the relation
between the original sensitive input and an attacker's observations.
Symbolic execution provides fine-grained information, but it is expensive
to compute. Therefore, prior symbolic
execution work~\cite{203878,236338,Brotzman19Casym} either analyzes only
small programs or applies domain knowledge~\cite{203878} to simplify the analysis. We
examine the bottleneck of the trace-oriented symbolic execution and optimize it
to work for real-world crypto-systems.

>>>>

\section{Problem}
In Chapter~\ref{chapter3}, we present a method to identify address-based side-channel leakage sites in cryptography libraries ~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}. However, many reported leakage sites are not patched by the developers. Recent work on side-channel vulnerability identification~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} also faced the same situation. For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@. Further analysis shows 1,510 leaks can be dismissed, but that still leaves 460 data-access leaks and 278 control-flow leaks. Many of these vulnerabilities have not been fixed by the developers for a variety of reasons.

First, some vulnerable implementations perform better. For example,
RSA implementations usually adopt the Chinese Remainder Theorem (CRT) optimization, which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}. Second, fixing vulnerabilities can introduce new
weaknesses. Third, most vulnerabilities pose a negligible risk. Although some vulnerabilities result in the key being entirely compromised~\cite{184415, aumuller2002fault}, many others are less severe in reality. Therefore, we need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.

@@

To overcome these limitations, we propose a novel method to quantify information
leakage precisely. We quantify the number of bits that can be leaked during a real
execution and define the amount of leaked information as the cardinality of
possible secrets based on an attacker's observation. Before an attack, an adversary has a large but finite input space.
Whenever the adversary observes a leakage site, he can eliminate some impossible
inputs and reduce the input space's size. In an extreme case, if the input space's size reduces to one, an adversary has determined the input, which means all secret information (e.g., the entire secret key) is
leaked. By counting the number of inputs~\cite{10.1007/11499107_24}, we can quantify the information leakage precisely.
We use symbolic execution to generate constraints to model the relation
between the original sensitive input and an attacker's observations.
Symbolic execution provides fine-grained information, but it is expensive
to compute. Therefore, prior symbolic
execution work~\cite{203878,236338,Brotzman19Casym} either analyzes only
small programs or applies domain knowledge~\cite{203878} to simplify the analysis. We
examine the bottleneck of the trace-oriented symbolic execution and optimize it
to work for real-world crypto-systems.
